%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% Revisions: 2017-04-10 Martin Rädel <martin.raedel@dlr.de>
%                       Initial draft
%               
% Contact:   Martin Rädel,  martin.raedel@dlr.de
%            DLR Composite Structures and Adaptive Systems
%          
%                                 __/|__
%                                /_/_/_/  
%            www.dlr.de/fa/en      |/ DLR
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Content                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\marktool{\paraviewname} is an open source multiple-platform application for interactive, scientific visualization. The current release and further informations can be found on

\href{\paraviewaddress}{\paraviewaddress}

\marktool{\paraviewname} was developed to analyze extremely large datasets using distributed memory computing resources.

\leveldown{Linux installation}

\paragraph{Use 1-click install}

Go to

\href{https://software.opensuse.org/download/package?project=science\&package=paraview}{https://software.opensuse.org/download/package?project=science\&package=paraview}

and choose 1-Click-Install or download the rpm-file from the source.

\paragraph{Installation with \marktool{\opensusename}-repository} \marktool{\paraviewname} is part of the \marktool{\opensusename} Science Repository. The repository can be included into the package management.

\begingroup
\lstset{breaklines=true}
\begin{code}
zypper addrepo http://download.opensuse.org/repositories/science/openSUSE_Leap_42.1/science.repo
zypper refresh
zypper install paraview
\end{code}
\endgroup

\paragraph{Installation from source} The source code of the current \marktool{\paraviewname} release is available from the download section of the \marktool{\paraviewname} homepage. For an installation using the source code and \marktool{\cmakename} please consult

\href{http://www.paraview.org/Wiki/ParaView:Build\_And\_Install}{http://www.paraview.org/Wiki/ParaView:Build\_And\_Install}

\levelstay{Windows installation}

Go to the download section of the \marktool[\paraviewaddress]{\paraviewname} homepage and download the binary installers for your windows operating system architecture. Afterwards, simply run the executable installer and follow the instructions.