\levelstay{Handling large result files in \protect\LaTeX}

\leveldown{Increase \TeX{}-memory}      \label{sec:Increase_TeX_Memory}

For large figures or plots of results using \verb+pgfplots+ the initial \TeX{} memory might be insufficient. A first possibility to solve that problem is to increase the \TeX{} memory.

\leveldown{MiKTeX on Windows}

\begin{itemize}[noitemsep]
\item Open a command prompt (cmd)
\item Type \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+initexmf --edit-config-file pdflatex+} and press Enter
\item A file pops up in the editor
\item Add \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+main_memory=8000000+} to the file
\item Save the file
\item Go back to the command prompt
\item Type \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+initexmf --dump=pdflatex+} and press Enter
\item After completion, close the command prompt
\end{itemize}

\levelstay{TeXLive on Linux}

Untested:

\begin{itemize}[noitemsep]
\item Open a terminal
\item Type \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+kpsewhich texmf.cnf+} and press Enter
\item This gives the path to the \verb+texmf.cnf+ file
\item Open the file
\item Change or add \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+main_memory=8000000+} to the file
\item Save the file
\item Go back to the command prompt
\item Type \colorbox{verbgray}{\lstinline[style=inlinetexstyle]+sudo fmtutil-sys --all+} and press Enter
\item After completion, close the command prompt
\end{itemize}

Be aware that using this method you modify the official config file which will be overwritten in an update. Thus, you have to repeat this step after an update. A better and update-independent solution is to create a local \verb+texmf.cnf+-file and register it in the \TeX{} path variables

\levelup{Externalize TikZ- \& pgfplots-figure creation} \label{sec:Externalize_Figure_Creation}

Creation of \lstinline[style=inlinetexstyle]+TikZ+ or \lstinline[style=inlinetexstyle]+pgfplotsset+-figures can be quite memory and time consuming. The creation of these figures can be externalized to save time. This means the figure is compiled once and written to a graphics file (pdf, png, ...). The next \lstinline[style=inlinetexstyle]+pdflatex+ run re-uses the created figure. It is not re-created for each compilation.

To achieve the externalization you need to add the following code to your preamble in addition to \lstinline[style=inlinetexstyle]+\usepackage{pgfplots}+:

\begingroup
\lstset{breaklines = true}
\lstinputlisting[
  style=texstyle,
  caption=TikZ externalization code,
  label=lst:TikZ_externalize,
  ]{\peridoccommonpath/Preamble/Pref_Packages_TikZ_Externalization}
\endgroup

\ifpdf
You can \textattachfile[author=raed_ma, color=0 0 1]{\peridoccommonpath/Preamble/Pref_Packages_TikZ_Externalization}{download} the file from within this document.
\fi

Using one of the last two lines of the \verb+tikzset+ converts the pdf file of the figure created by \verb+pdflatex+ to a png file. It requires the installation of \href{http://www.imagemagick.org/script/index.php}{ImageMagick} which provides the \verb+convert+ command for ImageMagick version prior to 7 or \verb+magick+ for version 7 or newer. For this to work, the path to the ImageMagick binaries \verb+convert.exe+ or \verb+magick.exe+ must be added to the system \texttt{PATH} environment variable.

In case you want to externalize the creation of a single figure add the following:

\begin{texcode}
\tikzexternalenable                     §\lstcomment{\% Enable externalization}§
\tikzsetnextfilename{Chart_Example}     §\lstcomment{\% Figure file name}§
\input{Figures/LaTeX/Chart_Example}     §\lstcomment{\% Path to figure}§
\tikzexternaldisable                    §\lstcomment{\% Disable externalization}§
\end{texcode}

Beware, if you make changes to a figure you have to delete the present figure file before compiling your document. Otherwise, the update will not be effective because the old figure is re-used.